---
title: "Modelisation predictive"
author: "Romain HU - Marine VIEILLARD"
date: "08/03/2025"
output:
  html_document: default
  pdf_document: default
---

```{r include=FALSE}
rm(list=objects())
setwd("C:/Marine/M1 Maths&IA/S2/Modélisation prédictive")
set.seed(13)
```

# Import and data processing

```{r include=FALSE}
library(tidyverse)
library(lubridate)
library(forecast)
library(mgcv)
library(yarrr)
library(magrittr)
library(ranger)
library(opera)
library(gbm)
library(caret)

library(randomForest)
library(xgboost)
library(neuralnet)
library(plsmselect)
library(qgam)
library("quantreg")

```

## Import Data

```{r}
source("score.R")
Data0 <- read_delim("Data/train.csv", delim=",", show_col_types	= FALSE)
Data1 <- read_delim("Data/test.csv", delim=",", show_col_types	= FALSE)
```

## Data processing

### Transform Date and WeekDays

```{r}
Data0$Time <- as.numeric(Data0$Date)
Data1$Time <- as.numeric(Data1$Date)

Data0$WeekDays <- as.factor(Data0$WeekDays)
Data1$WeekDays <- as.factor(Data1$WeekDays)
Data0$WeekDays2 <- weekdays(Data0$Date)
Data0$WeekDays2 <- forcats::fct_recode(Data0$WeekDays2, 'WorkDay'='jeudi' ,'WorkDay'='mardi', 'WorkDay' = 'mercredi')

```

```{r results='hide'}
head(Data0)
summary(Data0)
```

### Check missing values

```{r results = 'hide'}
sapply(Data0, function(x) sum(is.na(x)))
sapply(Data1, function(x) sum(is.na(x)))
```

### Creation of a validation set

```{r}
sel_a <- which(Data0$Year<=2021)
sel_b <- which(Data0$Year>2021)
```

## Data visualisation

### Trend

```{r results='hide', fig.show="hide"}
plot(Data0$Date, Data0$Net_demand, type='l', xlab = "Date", ylab = "Consumption")
lines(Data0$Date[sel_b], Data0$Net_demand[sel_b], col = "red",)
```

### One year representation

```{r}
plot(Data0$Date[1:365], Data0$Net_demand[1:365], type='l', xlab = "Date", ylab = "Consumption")

```

```{r results='hide', fig.show="hide"}
plot(Data0$toy, Data0$Net_demand, pch=16,  col=adjustcolor(col='black', alpha=0.3))
```

### Days representation

```{r results='hide', fig.show="hide"}
plot(Data0$Net_demand.1, Data0$Net_demand)
cor(Data0$Net_demand.1, Data0$Net_demand)
boxplot(Net_demand~WeekDays, data=Data0)
boxplot(Net_demand~BH, data=Data0)
```

### Meteo effect

```{r results='hide', fig.show="hide"}
plot(Data0$Date, Data0$Net_demand, type='l', xlab='', ylab='')
par(new=T)
plot(Data0$Date, Data0$Temp, type='l', col='red', axes=F,xlab='Date',ylab='')
legend("topright", legend=c("Net Demand","Temp"), col=c("black","red"), lty=1)

plot(Data0$Date[1:365], Data0$Net_demand[1:365], type='l', xlab='Date', ylab='')
par(new=T)
plot(Data0$Date[1:365], Data0$Temp[1:365], type='l', col='red', axes=F,xlab='',ylab='')
legend("topright", legend=c("Net Demand","Temp"), col=c("black","red"), lty=1)


plot(Data0$Temp, Data0$Net_demand, pch=3,  col=adjustcolor(col='black', alpha=0.25),xlab='Temperature', ylab='Net_demand')
```

### Autocorrelation

```{r }
Acf(Data0$Net_demand, lag.max=7*10, type = c("correlation"), col="blue", ylim=c(0,1))
Acf(Data0$Net_demand, lag.max=7*60, type = c("correlation"), col="blue", ylim=c(-1,1))

```

# First approach : Linear Model

```{r results = F}
############################################################
############### bloc cv
############################################################
Nblock<-8
borne_block<-seq(1, nrow(Data0), length=Nblock+1)%>%floor
block_list<-list()
l<-length(borne_block)
for(i in c(2:(l-1)))
{
  block_list[[i-1]] <- c(borne_block[i-1]:(borne_block[i]-1))
}
block_list[[l-1]]<-c(borne_block[l-1]:(borne_block[l]))



fitmod <- function(eq, block) #prend eq modèle et le block , fit sans bloc et predit sur bloc
{
  mod <- lm(eq, data=Data0[-block,])
  mod.cvpred <- predict(mod, newdata=Data0[block,])
  return(mod.cvpred)
}

####################################################################
################ Modèle linéaire
####################################################################
Data0$Temp_trunc1 <- pmax(Data0$Temp-286,0) #température - seuil , partie postive 
Data0$Temp_trunc2 <- pmax(Data0$Temp-290,0)

w<-2*pi/(365)
Nfourier<-50
for(i in c(1:Nfourier))
{
  assign(paste("cos", i, sep=""),cos(w*Data0$Time*i)) #asign assigner des valeurs à une chaine de caractère
  assign(paste("sin", i, sep=""),sin(w*Data0$Time*i))
}

cos<-paste('cos',c(1:Nfourier),sep="",collapse=",")                         
sin<-paste('sin',c(1:Nfourier),sep="",collapse=",")

Data0<-eval(parse(text=paste("data.frame(Data0,",cos,",",sin,")",sep="")))


#fait 30 modèles emboités
Nfourier<-30
lm.fourier<-list()
eq<-list()
for(i in c(1:Nfourier))
{
  cos<-paste(c('cos'),c(1:i),sep="")
  sin<-paste(c('sin'),c(1:i),sep="")
  fourier<-paste(c(cos,sin),collapse="+")
  eq[[i]]<-as.formula(paste("Net_demand~ WeekDays2 + Temp + Temp_trunc1 + Temp_trunc2+",fourier,sep=""))
  lm.fourier[[i]]<-lm(eq[[i]],data=Data0[sel_a,])
}



adj.rsquare<-lapply(lm.fourier,
                    function(x){summary(x)$adj.r.squared})%>%unlist

fit.rmse<-lapply(lm.fourier,
                 function(x){rmse(Data0$Net_demand[sel_a],x$fitted)})%>%unlist

forecast.rmse<-lapply(lm.fourier
                      , function(x){rmse(Data0$Net_demand[sel_b],predict(x,newdata=Data0[sel_b,]))})%>%unlist

fit.mape<-lapply(lm.fourier,
                 function(x){mape(Data0$Net_demand[sel_a],x$fitted)})%>%unlist

forecast.mape<-lapply(lm.fourier
                      , function(x){mape(Data0$Net_demand[sel_b],predict(x,newdata=Data0[sel_b,]))})%>%unlist

form <- eq[[10]]
form <- buildmer::add.terms(form, "Net_demand.1")
form <- buildmer::add.terms(form, "Net_demand.7")
```

```{r}
mod5 <- lm(form, data=Data0[sel_a,])
mod5.forecast <- predict(mod5, newdata=Data0[sel_b,])
summary(mod5)

rmse(y=Data0$Net_demand[sel_b], ychap=mod5.forecast) 

mod5.cvpred<-lapply(block_list, fitmod, eq=form)%>%unlist
rmse(y=Data0$Net_demand, ychap=mod5.cvpred)

res <- Data0$Net_demand - mod5.cvpred
quant <- qnorm(0.8, mean= mean(res), sd= sd(res))
pb5 <- pinball_loss(y=Data0$Net_demand[sel_b], mod5.forecast+quant, quant=0.8, output.vect=FALSE)
pb5 #638
```

```{r}
# prediction
Data1$WeekDays2 <- weekdays(Data1$Date)
Data1$WeekDays2 <- forcats::fct_recode(Data1$WeekDays2, 'WorkDay'='jeudi' ,'WorkDay'='mardi', 'WorkDay' = 'mercredi')

Data1$Temp_trunc1 <- pmax(Data1$Temp-286,0)
Data1$Temp_trunc2 <- pmax(Data1$Temp-290,0)

w<-2*pi/(365)
Nfourier<-50
for(i in c(1:Nfourier))
{
  assign(paste("cos", i, sep=""),cos(w*Data1$Time*i))
  assign(paste("sin", i, sep=""),sin(w*Data1$Time*i))
}

cos<-paste('cos',c(1:Nfourier),sep="",collapse=",")                         
sin<-paste('sin',c(1:Nfourier),sep="",collapse=",")

Data1<-eval(parse(text=paste("data.frame(Data1,",cos,",",sin,")",sep="")))


mod5final <- lm(form, data=Data0)

###prev moyenne
lm.forecast <- predict(mod5final, newdata=Data1)
###prev proba
res <- Data0$Net_demand - mod5.cvpred
quant <- qnorm(0.8, mean= mean(res), sd= sd(res))

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- lm.forecast+quant
write.table(submit, file="Data/submission_lm5.csv", quote=F, sep=",", dec='.',row.names = F)
```

Score obtained on Kaggle : 884

# Quantile regression

```{r}
mod5.rq <- rq(form, data = Data0[sel_a, ], tau=0.7) 
#summary(mod5.rq)

mod5.rq.forecast <- predict(mod5.rq, newdata=Data0[sel_b,])
pb_rq2 <- pinball_loss(y=Data0$Net_demand[sel_b], mod5.rq.forecast, quant=0.8, output.vect=FALSE)
pb_rq2 #555


mod5final <- rq(form, data = Data0, tau=0.7)
mod5final.forecast <- predict(mod5final, newdata=Data1)

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- mod5final.forecast
write.table(submit, file="Data/submission_rq5bis.csv", quote=F, sep=",", dec='.',row.names = F)
```

Score obtained on Kaggle : 830

# Ensemble method

```{r}
mod5 <- lm(form, data=Data0[sel_a,])
mod5.forecast <- predict(mod5, newdata=Data0[sel_b,])
#summary(mod5)
rmse(y=Data0$Net_demand[sel_b], ychap=mod5.forecast)

mod5.cvpred<-lapply(block_list, fitmod, eq=form)%>%unlist


fit.ensemble <- function(eq, block)
{
  mod <- lm(eq, data=Data0[-block,])
  mod.forecast <- predict(mod, newdata=Data1)
  return(mod.forecast)
}

mod5.ensemble <-lapply(block_list, fit.ensemble, eq=form)

mod5.ensemble <- mod5.ensemble%>%unlist%>%matrix(ncol=length(block_list), nrow=nrow(Data1), byrow=F)
mod5.ensemble%>%head
mod5.ensemble <- rowMeans(mod5.ensemble)


submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- mod5.ensemble
write.table(submit, file="Data/submission_lm_ensemble_block.csv", quote=F, sep=",", dec='.',row.names = F)
```

Score obtained on Kaggle : 637

# Random Forest

```{r}
Nblock <- 8
borne_block <- seq(1, nrow(Data0), length = Nblock + 1) %>% floor
block_list <- list()
l <- length(borne_block)
for (i in c(2:(l - 1))) {
  block_list[[i - 1]] <- c(borne_block[i - 1]:(borne_block[i] - 1))
}
block_list[[l - 1]] <- c(borne_block[l - 1]:(borne_block[l]))

fitmod_rf <- function(eq, block) {
  formula <- as.formula(eq)
  mod <- randomForest(formula, data = Data0[-block,], ntree = 100)
  mod.cvpred <- predict(mod, newdata = Data0[block,])
  return(mod.cvpred)
}


mod_rf3 <- randomForest(Net_demand ~ WeekDays2 + Temp + Net_demand.7 + Net_demand.1 + Month + Holiday, data = Data0[sel_a,])
mod_rf3.forecast <- predict(mod_rf3, newdata = Data0[sel_b,])
rmse(y = Data0$Net_demand[sel_b], ychap = mod_rf3.forecast)

residuals_rf3 <- Data0$Net_demand[sel_a] - mod_rf3$predicted

plot(Data0$Temp[sel_a], residuals_rf3, pch = 20)
g0 <- mgcv::gam(residuals_rf3 ~ s(Data0$Temp[sel_a]))
points(Data0[sel_a,]$Temp, g0$fitted, col = "red")

plot(Data0$Temp[sel_a], Data0$Net_demand[sel_a], pch = 20)
points(Data0$Temp[sel_a], mod_rf3$predicted, pch = 20, col = "red")

mod_rf3.cvpred <- lapply(block_list, fitmod_rf, eq = "Net_demand ~ WeekDays2 + Temp + Net_demand.7 + Net_demand.1 + Month + Holiday") %>% unlist
rmse(y = Data0$Net_demand, ychap = mod_rf3.cvpred)
res <- Data0$Net_demand - mod_rf3.cvpred
quant <- qnorm(0.8, mean = mean(res), sd = sd(res))
pb_rf3 <- pinball_loss(y = Data0$Net_demand[sel_b], mod_rf3.forecast + quant, quant = 0.8, output.vect = FALSE)
pb_rf3 #668


modfinal <- randomForest(Net_demand ~ WeekDays2 + Temp + Net_demand.7 + Net_demand.1 + Month + Holiday, data = Data0)
modf.cvpred <- lapply(block_list, fitmod_rf, eq = "Net_demand ~ WeekDays2 + Temp + Net_demand.7 + Net_demand.1 + Month + Holiday") %>% unlist

modf.forecast <- predict(modfinal, newdata=Data1, type = "response")

res <- Data0$Net_demand - mod_rf3.cvpred
quant <- qnorm(0.8, mean= mean(res), sd= sd(res))


submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- modf.forecast+quant
write.table(submit, file="Data/submission_rf.csv", quote=F, sep=",", dec='.',row.names = F)
```

Score obtained on Kaggle : 986

# Generalized Additive Model (GAM)

```{r eval=F }
equation <- Net_demand ~ s(as.numeric(Date),k=3, bs='cr') + s(toy,k=30, bs='cc') + s(Temp,k=10, bs='cr') + s(Load.1, bs='cr')+ s(Load.7, bs='cr') +
  s(Temp_s99,k=10, bs='cr') + WeekDays +BH +
  s(Wind) + s(Nebulosity)

gam_net4 <- gam(equation,  data=Data0[sel_a,])
sqrt(gam_net4$gcv.ubre)
gam_net4.forecast<-predict(gam_net4,  newdata= Data0[sel_b,])
rmse_net4.forecast <- rmse(Data0[sel_b,]$Net_demand, gam_net4.forecast)
res <- Data0$Net_demand[sel_b] - gam_net4.forecast
quant <- qnorm(0.95, mean= mean(res), sd= sd(res))
pinball_loss(y=Data0$Net_demand[sel_b], gam_net4.forecast+quant, quant=0.95, output.vect=FALSE) #179

mean(Data0[sel_b,]$Net_demand<gam_net4.forecast+quant)

hist(gam_net4$residuals, breaks=50)

gam_net4_sub <- gam(equation,  data=Data0)
sqrt(gam_net4_sub$gcv.ubre)
gam_net4_sub.forecast<-predict(gam_net4_sub,  newdata= Data1)

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- gam_net4_sub.forecast
write.table(submit, file="Data/submission_gam_net4.csv", quote=F, sep=",", dec='.',row.names = F)
```

Score obtained on Kaggle : 485

# QGAM

```{r}
equation <- Net_demand ~ s(as.numeric(Date),k=3, bs='cr') + s(toy,k=30, bs='cc') + s(Temp,k=10, bs='cr') + s(Load.1, bs='cr')+ s(Load.7, bs='cr') +
  s(Temp_s99,k=10, bs='cr') + WeekDays +BH +
  s(Wind) + s(Nebulosity)

qgam_model <- qgam(equation, data=Data0[sel_a,], qu=0.85)
qgam_forecast <- predict(qgam_model, newdata=Data0[sel_b,])
pinball_loss(y=Data0$Net_demand[sel_b], qgam_forecast, quant=0.85)
#291

qgam_net4_sub <- qgam(equation, data=Data0, qu=0.85)

qgam_net4_sub.forecast<-predict(qgam_net4_sub,  newdata= Data1)

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- qgam_net4_sub.forecast
write.table(submit, file="Data/submission_qgam85.csv", quote=F, sep=",", dec='.',row.names = F)
```

Score obtained on Kaggle : 750

# GAM with Arima

```{r include=FALSE, results=FALSE}
blockRMSE<-function(equation, block)
{
  g<- gam(as.formula(equation), data=Data0[-block,])
  forecast<-predict(g, newdata=Data0[block,])
  return(forecast)
} 

#equation used for the GAM
equation <- Net_demand ~ s(as.numeric(Date),k=3, bs='cr') + s(toy,k=30, bs='cc') + s(Temp,k=10, bs='cr') + s(Load.1, bs='cr')+ s(Load.7, bs='cr') +
  s(Temp_s99,k=10, bs='cr') + WeekDays +BH +
  s(Wind) + s(Nebulosity)

#Data preparation used for this model
Data0 <- read_delim("Data/train.csv", delim=",")
Data1<- read_delim("Data/test.csv", delim=",")
Data0$Time = as.numeric(Data0$Date)
Data1$Time = as.numeric(Data1$Date)
Data0$WeekDays <- as.factor(Data0$WeekDays)
Data1$WeekDays <- as.factor(Data1$WeekDays)
Data0$WeekDays2 <- weekdays(Data0$Date)
Data0$WeekDays2 <- forcats::fct_recode(Data0$WeekDays2, 'WorkDay'='jeudi' ,'WorkDay'='mardi', 'WorkDay' = 'mercredi')
Data1$WeekDays2 <- weekdays(Data1$Date)
Data1$WeekDays2 <- forcats::fct_recode(Data1$WeekDays2, 'WorkDay'='jeudi' ,'WorkDay'='mardi', 'WorkDay' = 'mercredi')

#block for Cross-Validation
Nblock = 10
borne_block = seq(1, nrow(Data0), length=Nblock+1)%>%floor
block_list = list()
l = length(borne_block)
for (i in c(2:(l-1)))
{
  block_list[[i-1]] = c(borne_block[i-1]:(borne_block[i]-1))
}
block_list[[l-1]] = c(borne_block[l-1]:(borne_block[l]))

gam_model<-gam(equation, data=Data0)

#First prediction for our Data to predict
gam.forecast.sub<-predict(gam_model,  newdata= Data1)

#Calibrating the arima model using Cross Validation to have unbiaised residuals. Using auto.arima
Block_forecast<-lapply(block_list, blockRMSE, equation=equation)%>%unlist
Block_residuals <- Data0$Net_demand-Block_forecast
Block_residuals.ts <- ts(Block_residuals, frequency=7)
fit.arima.res <- auto.arima(Block_residuals.ts,max.p=3,max.q=4, max.P=2, max.Q=2, trace=T,ic="aic", method="CSS")

#We then proceed to treat residuals for our prediction
ts_res_forecast <- ts(c(Block_residuals.ts, Data1$Net_demand.1 - gam.forecast.sub),  frequency= 7)
refit <- Arima(ts_res_forecast, model=fit.arima.res)

prevARIMA.res <- tail(refit$fitted, nrow(Data1))

#Adding the arima correction to the original prediction
gam.forecast.sub <- gam.forecast.sub + prevARIMA.res

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- gam.forecast.sub
write.table(submit, file="Data/submission_gamari2.csv", quote=F, sep=",", dec='.',row.names = F)
```

Score obtained on Kaggle : 703

# Online GAM model with Arima

```{r include=FALSE ,eval = FALSE}
blockCV = function(Data)
{
  Nblock = 10
  borne_block = seq(1, nrow(Data), length=Nblock+1)%>%floor
  block_list = list()
  l = length(borne_block)
  for (i in c(2:(l-1)))
  {
    block_list[[i-1]] = c(borne_block[i-1]:(borne_block[i]-1))
  }
  block_list[[l-1]] = c(borne_block[l-1]:(borne_block[l]))
  return(block_list)
}

#equation we will use for all the gam models used
equation <- Net_demand ~ s(as.numeric(Date),k=3, bs='cr') + s(toy,k=30, bs='cc') + s(Temp,k=10, bs='cr') + s(Load.1, bs='cr')+ s(Load.7, bs='cr') +
  s(Temp_s99,k=10, bs='cr') + WeekDays +BH +
  s(Wind) + s(Nebulosity)

equation <- Net_demand ~ s(as.numeric(Date),k=3, bs='cr') + s(toy,k=30, bs='cc') + s(Temp,k=10, bs='cr') + s(Net_demand.1, bs='cr')+ s(Net_demand.7, bs='cr') +
  s(Temp_s99,k=10, bs='cr') + WeekDays +BH +
  s(Wind) + s(Nebulosity)


gam9<-gam(equation, data=Data0)

gam.forecast.sub<-predict(gam_model,  newdata= Data1)

Block_forecast<-predict(gam_model,newdata=Data0)
Block_residuals <- Data0$Net_demand-Block_forecast

Block_residuals.ts <- ts(Block_residuals, frequency=7)

gam.forecast_update <- gam.forecast.sub

#Data_set that will contain all available data (=past data)
Past_Data = tibble(Data0)


for(i in 1:(nrow(Data1)-1)) {
  # Création d'une copie de la ligne actuelle
  line_merged <- Data1[i,]  
  
  # Remplacement de Net_demand par Net_demand.1[i+1]
  line_merged$Net_demand <- Data1$Net_demand.1[i+1]
  
  # Ajout à la base de données
  Past_Data <- bind_rows(Past_Data, line_merged)  # Utilisation de `bind_rows()` pour éviter les problèmes de structure
  
  # Réentraîner le modèle avec les nouvelles données
  gam_model <- gam(equation, data=Past_Data)
  
  # Prédire le jour suivant avec GAM
  intermediate <- predict(gam_model, newdata=Data1[i+1,])
  
  # Calcul des résidus sur la nouvelle base de données
  Block_residuals <- Past_Data$Net_demand - predict(gam_model, newdata=Past_Data)
  Block_residuals.ts <- ts(Block_residuals, frequency=7)
  
  # Ajustement ARIMA
  fit.arima.res <- auto.arima(Block_residuals.ts, max.p=3, max.q=4, max.P=2, max.Q=2, trace=T, ic="aic", method="CSS")
  
  # Correction avec ARIMA
  ts_res_forecast <- ts(c(Block_residuals.ts, Data1$Load.1[i+1] - intermediate))
  refit <- Arima(ts_res_forecast, model=fit.arima.res)
  prevARIMA.res <- tail(refit$fitted, 1)
  
  # Mise à jour de la prédiction
  gam.forecast_update[i+1] <- intermediate + prevARIMA.res
  
  print(i)
}

print(gam.forecast_update)

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- gam.forecast_update
write.table(submit, file="Data/submission_gamarion1.csv", quote=F, sep=",", dec='.',row.names = F)

```

Score on Kaggle : 479

# Online Random Forest

```{r include = FALSE, eval=FALSE}
set.seed(13)

equation_forest <- Net_demand ~ WeekDays2 + Temp + Net_demand.7 + Net_demand.1 + Month + Holiday


#bloc CV
Nblock = 10
borne_block = seq(1, nrow(Data0), length=Nblock+1)%>%floor
block_list = list()
l = length(borne_block)
for (i in c(2:(l-1)))
{
  block_list[[i-1]] = c(borne_block[i-1]:(borne_block[i]-1))
}
block_list[[l-1]] = c(borne_block[l-1]:(borne_block[l]))


rf <- ranger(equation_forest, data=Data0)
rf.forecast <-  predict(rf, data=Data1)$predictions

rf.forecast_update <- rf.forecast
Past_Data = tibble(Data0)


for(i in c(1: (nrow(Data1)-1))) {
  # Créer une copie exacte de Data1[i,]
  line_merged <- Data1[i,]
  
  # Remplacer uniquement la valeur de Net_demand
  line_merged$Net_demand <- Data1$Net_demand.1[i+1]
  
  # Ajouter la nouvelle ligne dans Past_Data
  Past_Data <- bind_rows(Past_Data, line_merged)  # bind_rows() évite les erreurs de structure
  
  # Réentraîner le modèle
  rf <- ranger::ranger(equation_forest, data=Past_Data)
  
  # Faire une nouvelle prédiction
  rf.forecast_update[i+1] <- predict(rf, data=Data1[i+1,], predict.all = F)$predictions
}

print(rf.forecast_update)

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- rf.forecast_update
write.table(submit, file="Data/submission_rfon2.csv", quote=F, sep=",", dec='.',row.names = F)
# 755 sur kaggle (rfon2)
```

Score on Kaggle : 755

# Boosting

```{r, include=FALSE}
equation_boosting = Net_demand ~ WeekDays2 + Temp + Net_demand.7 + Net_demand.1 + Month + Holiday 

model_gbm = gbm(formula = equation_boosting,data = Data0,distribution="gaussian",
                cv.folds = 10,shrinkage=0.01, n.trees = 1500)

pred_y = predict.gbm(model_gbm, Data1)

submit <- read_delim( file="Data/sample_submission.csv", delim=",")
submit$Net_demand <- pred_y
write.table(submit, file="Data/submission_boost1.csv", quote=F, sep=",", dec='.',row.names = F)
# 678  sur kaggle (boost1)
```

Score on Kaggle : 678
